---
title: "Motor Trend"
author: "Shikhar"
date: "17/09/2020"
output: 
  html_document:
       keep_md: yes
---

# Summary
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

## 1. “Is an automatic or manual transmission better for MPG”
## 2. "Quantify the MPG difference between automatic and manual transmissions"
### Preprocessing the data

This is the preprocessing of data.

```{r cars}
setwd("D:/R/Class/6Inferential Statistics/Project")
library(datasets)
data(mtcars)
names(mtcars)
nrow(mtcars); ncol(mtcars)
summary(mtcars)
```

### Q1. Is an automatic or manual transmission better for MPG?

```{r}
t.test(mtcars$mpg~mtcars$am)$p.value
```
Here, we checked the P-values which are less than 0.05. Thus, we can reject the NULL hypothesis. So we conclude that automatic cars have lower transmission than that of manual cars, when all other conditions remain ideally same.

### Q2. Quantify the MPG difference between automatic and manual transmissions.


```{r}
linreg <- lm(data=mtcars,mpg~.)
stp <- step(linreg,direction="both")
summary(stp)
```
#### Following are the conclusions drawn :
the model here has a 89.5% variance with adjusted variance of 0.879.
1. when the weight is increased by 1000lbs then mpg decreases by -3.176 for automatic transmission cars, and by -6.09 for manual transmission cars
2. so with increasing car weight we should choose manual transmission cars
3. when the acceleration speed dropped, and 1/4 mile time increased (by 1 sec), the mpg factor increased by 0.834 miles for automatic transmission cars, and 1.446 miles for manual transmission cars
4. so with lower acceleration speed, but same weight, manual transmission cars are better for mpg


## Appendix

```{r}
pairs(mtcars)
```

```{r}
par(mfrow=c(2,2))
plot(stp,main="Residuals and Diagnostics")
```

```{r}
boxplot(mtcars$mpg~mtcars$am,mtcars,xlab="Type",ylab="Miles Per Gallon",main="O means automatic and 1 means manual",col="maroon")
```